Kyoto VR MQP Paper First Draft

### 2019-09-09 paper.tex
got rid of euro compile issue

% useful packages
\usepackage[utf8]{inputenc}
\usepackage{minted}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{graphicx} % for images

@@

From all of this information, Wikitude certainly sounds like a fantastic AR development
platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
fact, free for eligible startups, but given the criteria they list on their site, we were not
confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
license for €499, which is a lot for use to pay for a license that wouldn't even last for
our entire project. They also charge €1990 for their SDK Pro, and €2490 for their
SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget
of \$0, we knew that we would have to pass on Wikitude and choose a different AR
development platform.

>>>>

% useful packages
\usepackage[utf8]{inputenc}
\usepackage{minted}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol

@@

From all of this information, Wikitude certainly sounds like a fantastic AR development
platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
fact, free for eligible startups, but given the criteria they list on their site, we were not
confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
license for \euro{499}, which is a lot for use to pay for a license that would not even last for
our entire project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for their
SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget
of \$0, we knew that we would have to pass on Wikitude and choose a different AR
development platform.
